### 2020-12-07 doc/manuscript/Dow_manuscript.Rmd
work on discussion

We found that warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity...

Although the number of years analyzed here is limited (# years at SCBI, # years at HF), the signal is clear and consistent: for both species groups at both sites, warmer temperatures during virtually any part of the spring led to significantly earlier achievement of growth milestones (*CITE RELEVANT FIGS & TABLES* ).
This indicates that this is not a subtle effect.
However, the effect on L_PGS, r_max, and $\Delta DBH$, if any, is subtle, and a much longer record would be needed to detect such effects. 
Fortunately, we were able to get at annual growth using tree-ring data (Fig. `r tree_rings`).
These confirm that the effect of spring temperatures on annual growth is modest and generally not significant, while revealing a slightly more complex picture.
Although spring temperatures prior to May rarely had a significant influence on ...

THe tree-rings also reveal that the strongest temperature sensitivity aligned with peak growing season.
This pattern is common across tree-ring studies in temperate deciduous forests.
(*1-2 sentences generalizing about climate sensitivity of temperate deciduous forest growth--Neil can do this most easily.*)
Thus, while our analysis is limited to two sites, we expect that the finding that spring temperatures have limited effect on annual tree growth will hold generally.

Our findings contribute to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (REFS), an earlier start to net C sequestration (REFS), and--as shown here--earlier initiation of stem growth (*CITE RELEVANT FIGS & TABLES* ).
Yet, an earlier start to the growing season does not imply a longer growing season [Table `r hypothesis_table`, Figs `r pheno_Tsensitivity`, `r DOYtiming`;  @zani_increased_2020].
Rather, growth finishes sooner-- presumably because of *C sink limitation* [@zani_increased_2020].
As sink limitation controls the end of woody growing season [@zani_increased_2020], we might expect that an earlier start to growth buffers against unfavorable growth conditions during the peak growing season (e.g., drought).
*Do we see any evidence of this???*

@@

~~~~
## Cam's previous content

>>>>

We found that warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity.

Although the number of years analyzed here is limited (# years at SCBI, 6 years at HF), the signal is clear and consistent: for both species groups at both sites, warmer temperatures during virtually any part of the spring led to significantly earlier achievement of growth milestones (Table `r hypothesis_table`, Figs. `r  climwin`-`r DOYtiming`).
This indicates that the effect of $T_{max}$ on the timing of growth ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$,and $DOY_{g_{max}}$) is not subtle; 
indeed, growth milestones advanced by #-# days per degree Celsius during the critical temperature window.
This is consistent with previous studies showing that ... *(find/cite some statistics on how rapidly leaf phenology or start of C sequestration advance with T)*

In contrast to the pronounced effects of $T_{max}$ on the timing of growth, its effects on $g_{max}$ and $\Delta DBH$ were less consistent and generally quite subtle (Table `r hypothesis_table`, Fig. `r pheno_Tsensitivity`), such that a much longer record would be needed to clarify what, if any, effect spring temperatures have on maximum daily and annual growth rates. 
Fortunately, we were able to use tree-ring data to understand centennial-scale temperature sensitivity of annual growth (Fig. `r tree_rings`).
This analysis confirms that the effect of spring temperatures on annual growth is modest and not statistically significant for most species, while revealing a slightly more complex picture.
It appears that temperatures--particularly $T_{max}$--during one spring month at each site (April at SCBI, May at Harvard Forest) consistently have a weakly positive (*albiet* rarely significant) effect on annual growth, in striking contrast to the predominantly negative correlations of growth rates with $T_{max}$ in preceding and subsequent months.
This suggests that spring $T_{max}$, though it's pronounced influence on the start of woody growth and subtle influence on length of the peak growing season, has a modestly positive influence on annual tree growth, but that this influence is generally of secondary importance to other factors.

Indeed, the tree-ring records reveal that at SCBI the strongest temperature sensitivity aligned with peak growing season [@helcoski_growing_2019], whereas there were fewer significant climate correlations for the species at Harvard Forest (Fig. `r tree_rings`).
Relative to other temperate deciduous forest sites, the pattern at SCBI tends to be more typical: annual growth is most commonly controlled by climate conditions during the peak growing season.
(*1-2 sentences generalizing about climate sensitivity of temperate deciduous forest growth--Neil can do this most easily.*)
Thus, while our analysis is limited to two sites, we expect that the finding that spring temperatures have limited effect on annual tree growth will hold generally.

Our findings contribute to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (REFS), an earlier start to net C sequestration (REFS), and--as shown here--earlier initiation of stem growth (Figs. `r climwin`- `r DOYtiming`).
Yet, an earlier start to the growing season does not imply a longer growing season [Table `r hypothesis_table`, Figs. `r pheno_Tsensitivity`, `r DOYtiming`;  @zani_increased_2020].
Rather, growth finishes sooner-- presumably because of *C sink limitation* [@zani_increased_2020].

@@

~~~~

## Cam's previous content
